Constrained Optimization-Based Neuro-Adaptive Control (CoNAC) for Uncertain Euler-Lagrange Systems Under Weight and Input Constraints

### 2025-03-29 manuscript.tex
table change
new table

The Euler-Lagrange system \eqref{eq:sys1} satisfy some important physical properties \cite[see, Chap. 3 Tab. 3.2.1]{Lewis:1998aa}.
We introduce the following properties:
\begin{prop} \cite{Lewis:1998aa}
    The inertia matrix $\mm M$ is symmetric, positive definite and bounded.
    \label{prop:M}
\end{prop}

\begin{prop} \cite{Lewis:1998aa}
    The Coriolis/centripetal matrix $\mm V_m$ can always be selected so that the matrix $(\dot{\mm M}-2\mm V_m)$ is skew-symmetric.
    \label{prop:skew}
\end{prop}

@@

The DNN architecture $\NN_k = \NN(\q_{NN};\wth)$ can be recursively represented as follows:
\begin{equation}
    \NN_i :=
    \begin{cases}
        \wV_i^\top \NN_i(\NN_{i-1}), 
        &
        i\in[1,\dots,k],
        \\
        \wV_0^\top \q_{NN},
        &
        i=0
        ,
    \end{cases}
    \label{eq:DNN:architecture}
\end{equation}
where $\wV_i\in\R^{(l_i+1)\times l_{i+1}}$ is the weight matrix of the $i\textsuperscript{th}$ layer, and $\act_i: \R^{l_i}\to\R^{l_i+1}$ represents the activation function of the $i\textsuperscript{th}$ layer. 
The activation function is defined as $\act_i(\mv x)=[\sigma(x_1),\sigma(x_2),\cdots, \sigma(x_{l_{i}}), 1]^\top,\ \forall\mv x\in\R^{l_i}$, where $\sigma: \R\to\R$ is a nonlinear function, and the augmentation of $1$ is used to account for bias terms in the weight matrices. 
Notice that the output size of $\NN(\cdot)$ is the same as that of the control input $\mv\tau$ (\ie $l_{k+1}=n$).

@@

\begin{remark}
    Assumption \ref{assum:convex} is not restrictive, since the saturaion functions are convex in practice including the origin.
    Moreover, Assumption \ref{assum:LICQ} is a standard assumption in optimization problems, which ensures that the gradients of the active constraints are linearly independent.
    This assumption will be used in the stability analysis (see, Lemma \ref{lem:convex:angle}).
\end{remark}

@@

The weight constraints are essential to prevent the weights from diverging during the adaptation process.
The weight constraints $\boldsymbol{c}_{\theta}:= [c_{\theta_i}]_{i\in[0,\cdots ,k]}\in\mathbb R^{k+1}$ are defined for each layer's weight as follows:
\begin{equation}
    c_{\theta_i}
    =
    \tfrac{1}{2}
    (
        \Vert \estwth_i\Vert^2 
        -
        \bar\theta_i^2 
    )    
    \le 0
    \label{eq:cstr:weight_ball}
\end{equation}
with $\bar\theta_i<\infty$ denoting the maximum allowable norm for $\estwth_i$. 
The gradient of $\boldsymbol{c}_\theta$ with respect to $\estwth$ is given by
\begin{equation}
    \pptfrac{c_{\theta_i}}{\estwth_j} 
    =
    \begin{cases}
        \estwth_i,
        &
        \text{if } i=j
        \\
        0,
        &
        \text{if } i\ne j
        .
    \end{cases} 
    \label{eq:cstr:weight_ball:grad}
\end{equation}
Note that $\mv c_{\theta}$ satisfies Assumption \ref{assum:convex} and \ref{assum:LICQ} invoking Lemma \ref{lem:convex:angle} and \eqref{eq:cstr:weight_ball:grad}, respectively.

@@

Since, here, the control input constraints are inactive, $\mysat(\cdot)$ in \eqref{eq:lya1:dot2} and $c_j,\ \forall j\in\mathcal{I}$ in \eqref{eq:lya2:dot} can be removed.
Consider the Lyapunov function candidate $V_3:=V_1+V_2$ and its time derivative:
\begin{equation}
    \begin{aligned}
        \ddtt V_3
        =&
        -\lambda_{\text{min}}(\mm K)\norm{\fe}^2
        +\bar\tau_d\norm{\fe}
        +\fe^\top (\estNN - \idealNN - \mv\epsilon)
        \\
        &
        -\estwth_k^\top (
            (\mm I_{l_{k+1}}\otimes \hat\act_k^\top)^\top
            \fe
            +
            \lambda_{\theta_k}\estwth_k
        )
        \\
        \le&
        -\lambda_{\text{min}}(\mm K)\norm{\fe}^2
        +\fe^\top \estNN
        +(
            \bar\tau_d+\norm{
                \underbrace{
                    \idealNN+\mv\epsilon
                }_{=\mv\tau^*}
            }
        )
        \norm{\fe}
        \\
        &
        -\estNN^\top\fe 
        -\lambda_{\theta_k}\norm{\estwth_k}^2
        \\
        \le&
        -\lambda_{\text{min}}(\mm K)\norm{\fe}^2
        +\fe^\top \estNN
        +(\bar\tau_d+\bar\tau)
        \norm{\fe}
        -\lambda_{\theta_k}\norm{\estwth_k}^2
        .
    \end{aligned}
    \label{eq:lya3:dot}
\end{equation}
Like in Case (C$_1$), the boundedness of $\fe$ can be verified by the invariant sets $\Theta_{\fe}^{c_2}$ defined as
\begin{equation}
    \Theta_{\fe}^{c_2}
    =
    \left\{ 
        \fe \in \R^n 
        \mid 
        \norm{\fe} 
        \le 
        \tfrac{
            \bar\tau_d+\bar\tau
        }{
            \lambda_{\text{min}}(\mm K)
        }
    \right\}
    .
\end{equation}
The boundedness of $\estwth_k$ also can be ensured by the invariant set $\Theta_{\theta_k}^{c_2}=\{ \estwth_k \in \R^{\Xi_{k}} \mid \norm{\estwth_k} \le \bar\theta_k \}$, as $\lambda_{\theta_k}$ exists positive until $c_{\theta_k}$ is satisfied.

@@

The proposed CoNAC was validated using a two-link manipulator model, as depicted in Fig.~\ref{fig: manipulator}, adapted from \cite{Markus:2013aa}. 
The parameters $q_p,{q_d}_p,\tau_p,m_p,l_p,{l_c}_p,b_p$, and ${f_c}_p$ denote the joint angle, desired joint angle, torque, mass, length, center of mass, viscous coefficient, and friction coefficient, respectively, for link $p\in[1,2]$.
%This model contains terms of gravity and friction in its mechanical system.
%These terms make system functions in \eqref{eq. system dynamics 1} nonlinear.
%and can be considered as the disturbance of the system.
The values of the system model parameters are provided in Table~\ref{table: system parameters}. The desired trajectory for ${q}=[q_1,q_2]^\top$ was defined as
\begin{equation}
    {q_d}(t) = 
    \begin{bmatrix}
        {q_d}_1\\{q_d}_2
    \end{bmatrix}
    =
    \begin{bmatrix}
        +\cos(0.5\pi t) + 1 \\
        -\cos(0.5\pi t) - 1 
    \end{bmatrix}.
\end{equation}
%\color{red}
%Considering the power limitation of the power source for the actuators [], 
The control input saturation function was defined as $h(\tau):= \tau/\Vert\tau\Vert \cdot \text{SSF}_L^U(\Vert\tau\Vert)$, where smooth saturation function (SSF) was adopted from \cite{Vasquez-Plaza:2023aa} and is given by
\begin{equation}
    \text{SSF}_L^U(\Vert\tau\Vert) = {\Vert\tau\Vert\over (1+(\Vert\tau\Vert/\bar\tau)^p)^{1/p}}.
    \label{eq. h func}
\end{equation}
with $p$ being the smoothing factor. The effect of $p$ and the boundedness of $\Vert\partial h/\partial \tau\Vert_F$ is shown in Fig.~\ref{fig: h func}.
The parameters of the control input saturation function were selected as $p=100$ and $\bar\tau=50$.

@@

\begin{table}[!t]
    \renewcommand{\arraystretch}{1.3}
    \caption{System model parameters.}
    \label{table: error norm}
    \centering
    \begin{tabular}{|c||c|c|c|c|}
    \hline
    Symbol & \textbf{Description} & \textbf{Link 1} & \textbf{Link 2} \\
    \hline 
    $m_1, m_2$ & Mass of link    & 23.902 (kg) & 3.88 (kg) \\
    \hline
    $l_1, l_2$  & Length of link   & 0.45 (m) & 0.45 (m) \\
    \hline
    $l_{c1}, l_{c2}$ & COM of link  & 0.091 (m) & 0.048 (m) \\
    \hline
    $b_1, b_2$   & Viscous coefficient  &  2.288 (Nms) & 0.172 (Nms) \\
    \hline
    $f_{c1}, f_{c2}$  & Friction coefficient &  7.17 (Nm) & 1.734 (Nm) \\
    \hline
    \end{tabular}
    \label{table: system parameters}
\end{table}

@@

% **********************************************************
% SIMULATION FIGURES
\begin{figure*}[!t]
    \centering
        \subfloat[BSC]{\includegraphics[width=0.49\linewidth]{fig/fig1.eps}%
        \label{fig: tracking_CM1}}
    \hfill
        \subfloat[DNN-BSC]{\includegraphics[width=0.49\linewidth]{fig/fig2.eps}%
        \label{fig: tracking_CM2}}
    \vfill
        \subfloat[DNN-BSC-A]{\includegraphics[width=0.49\linewidth]{fig/fig3.eps}%
        \label{fig: tracking_CM3}}
    \hfill
        \subfloat[CoNAC]{\includegraphics[width=0.49\linewidth]{fig/fig4.eps}%
        \label{fig: tracking_CoNAC}}
    \caption{Comparison of the tracking performance across the selected controllers.}
    \label{fig: tracking}
\end{figure*}

\begin{figure*}[!t]
    \centering
        \subfloat[BSC]{\includegraphics[width=0.49\linewidth]{fig/fig5.eps}%
        \label{fig: control_CM1}}
    \hfill
        \subfloat[DNN-BSC]{\includegraphics[width=0.49\linewidth]{fig/fig6.eps}%
        \label{fig: control_CM2}}
    \vfill
        \subfloat[DNN-BSC-A]{\includegraphics[width=0.49\linewidth]{fig/fig7.eps}%
        \label{fig: control_CM3}}
    \hfill
        \subfloat[CoNAC]{\includegraphics[width=0.49\linewidth]{fig/fig8.eps}%
        \label{fig: control_CoNAC}}
    \caption{Comparison of the control input $\tau$ and the physically saturated control input $h(\tau)$ across the selected controllers.}
    \label{fig: control}
\end{figure*}

\begin{figure}[!t]
    \centering
    {\includegraphics[width=0.9\linewidth]{fig/fig16.eps}
    \caption{Control input paths of DNN-BSC and CoNAC during the time interval from 5 s to 8 s.}
    \label{fig: ball control}}
\end{figure}

\begin{figure*}[!t]
    \centering
        \subfloat[Multipliers of CoNAC]{\includegraphics[width=0.49\linewidth]{fig/fig12.eps}%
        \label{fig: multiplier_CoNAC}}
    \hfill
        \subfloat[Weight norms of DNN-BSC]{\includegraphics[width=0.49\linewidth]{fig/fig9.eps}%
        \label{fig: weight_CM2}}
    \vfill
        \subfloat[Weight norms of DNN-BSC-A]{\includegraphics[width=0.49\linewidth]{fig/fig10.eps}%
        \label{fig: weight_CM3}}
    \hfill
        \subfloat[Weight norms of CoNAC]{\includegraphics[width=0.49\linewidth]{fig/fig11.eps}%
        \label{fig: weight_CoNAC}}       
    \caption{Lagrange multipliers of CoNAC and weight norms of DNN-BSC, DNN-BSC-A, and CoNAC.}
    \label{fig: weight and multiplier}
\end{figure*}
% SIMULATION FIGURES
% **********************************************************

@@

The tracking results of the selected controllers are shown in Fig.~\ref{fig: tracking}.
To demonstrate the effectiveness of using DNNs for compensating the lumped system uncertainty function $f$, the gains ${k_q}$ and ${k_z}$ for BSC were intentionally selected as small values, resulting in a weak ability to handle these uncertainties. As a result,
%poor performance and sufficiently large values to satisfy \eqref{eq. ctrl stable condition}.
%the parameters of CM1 are poorly tuned, 
BSC failed to track the reference trajectory, as shown in Fig.~\ref{fig: tracking_CM1}.

@@

%Since it is generally known that the deeper NNs have better approximation performance with less computation cost, the NNs should have more layers.
%However, because the NNs in this paper utilize $\tanh(\cdot)$ as the activation function, the NNs have the gradient vanishing problem as shown in Fig.~\ref{fig: weight_CM2}-\ref{fig: weight_CoNAC}. (\ie the weight updates are smaller as its layer is closer to the input layer.)
%To address this issue, the activation function should be selected as the ReLU or the Leaky ReLU, while ensuring the stability of the controller.

@@

Most physical systems have control input limits due to electrical and mechanical limitations. These are expressed as $\boldsymbol{c}_{\overline \tau}:= [c_{\overline \tau_i}]_{i\in[1,\cdots,n]}$ and $\boldsymbol{c}_{\underline\tau}:= [c_{\underline\tau_i}]_{i\in[1,\cdots,n]}$, where
\begin{equation}
    \begin{aligned}
        c_{\overline \tau_i}=\tau_{(i)} - {\tau_{\overline \tau_i}} \le 0
        \\
        c_{\underline\tau_i}={\tau_{\underline\tau_i}}-\tau_{(i)} \le 0
    \end{aligned}
    \label{eq. cstr input saturation}
\end{equation}
with $\tau_{\overline \tau_i}$ and $\tau_{\underline\tau_i}$ representing the maximum and minimum control input bounds, respectively.
% The corresponding Lagrange multipliers are $\lambda_{u_j,i},\ \forall j\in[M,m]$. 
The gradients of $\boldsymbol{c}_{\overline \tau}$ and $\boldsymbol{c}_{\underline\tau}$ with respect to $\estwth$ are given by
\begin{equation}
    \begin{aligned}
        {\partial \boldsymbol c_{\overline \tau} \over \partial \estwth}
        =& 
        \begin{bmatrix}
            (\partial c_{\overline \tau_1}/\partial \estwth)^\top \\
            \vdots \\
            (\partial c_{\overline \tau_n}/\partial \estwth)^\top
        \end{bmatrix}
            = -{\partial \estNN\over\partial\estwth}
            \\
        =&
        -\begin{bmatrix}
            (I_{l_{k+1}}\otimes \estNN_{k}^\top)&
            % V_k^\top \phi_{k}' (I_{l_{k}}\otimes  \phi_{k-1}^\top)&
            \cdots &
            (
            \cdot
            )
        \end{bmatrix} 
        &
        \in
        \mathbb R^{n\times \Xi}
        , 
        \\
        {\partial \boldsymbol c_{\underline\tau} \over \partial \estwth}         
        :=
        & 
        \begin{bmatrix}
            (\partial c_{\underline\tau_1}/\partial \estwth)^\top \\
            \vdots \\
            (\partial c_{\underline\tau_n}/\partial \estwth)^\top
        \end{bmatrix}
        = +{\partial \estNN\over\partial\estwth}
        \\
        =&
        +\begin{bmatrix}
            (I_{l_{k+1}}\otimes \estNN_{k}^\top)&
            % V_k^\top \phi_{k}' (I_{l_{k}}\otimes  \phi_{k-1}^\top)&
            \cdots &
            (
            \cdot
            )
        \end{bmatrix} 
        &
        \in
        \mathbb R^{n\times \Xi}
        .
    \end{aligned}
    \label{eq. nabla input sat}
\end{equation}

@@

Consider the control input $\tau$ as the torque of each actuator corresponding to its generalized coordinate. Since torque is typically linearly proportional to current, actuators that share a common power source are often subject to total current limitations. This can be captured by the following inequality constraint: 
\begin{equation}
    c_{u}=\Vert\tau\Vert^2 -\bar\tau^2  \le 0
    \label{eq. cstr input ball}
\end{equation}
with $\bar\tau\in\R_{>0}$ denoting the maximum allowable control input magnitude. This input norm constraint is also commonly applied in current and torque control problems for electric motors \cite{Choi:2024aa}.
% The corresponding Lagrangian multipier is $\lambda_{u_b}$. 
The gradients of $c_{u}$ with respect to $\estwth$ are given by
\begin{equation}
    {\partial \boldsymbol c_{u} \over \partial \estwth}
    = -\sum_{i=1}^n 2\tau_{(i)} 
    \bigg(
        \myrow_i
        \bigg(
            -{\partial \estNN\over\partial\estwth}
        \bigg)
    \bigg)^\top  
    = \tau^\top (I_{l_{k+1}}\otimes \estNN_k^\top)
    \in \mathbb R^{\Xi}.
    \label{eq. nabla input ball}
\end{equation}
It should be noted that constraints \eqref{eq. cstr input saturation} and \eqref{eq. cstr input ball} cannot be imposed simultaneously, as their gradients \eqref{eq. nabla input sat} and \eqref{eq. nabla input ball} are linearly dependent, violating the LICQ condition.

>>>>

The Euler-Lagrange system \eqref{eq:sys1} satisfy some important physical properties \cite[see, Chap. 3 Tab. 3.2.1]{Lewis:1998aa}.
We introduce the following properties:
\begin{prop} 
    The inertia matrix $\mm M$ is symmetric, positive definite and bounded.
    \label{prop:M}
\end{prop}

\begin{prop} 
    The Coriolis/centripetal matrix $\mm V_m$ can always be selected so that the matrix $(\dot{\mm M}-2\mm V_m)$ is skew-symmetric.
    \label{prop:skew}
\end{prop}

@@

The DNN architecture $\NN(\q_{NN};\wth) := \NN_k$ can be recursively represented as follows:
\begin{equation}
    \NN_i :=
    \begin{cases}
        \wV_i^\top \NN_i(\NN_{i-1}), 
        &
        i\in[1,\dots,k],
        \\
        \wV_0^\top \q_{NN},
        &
        i=0
        ,
    \end{cases}
    \label{eq:DNN:architecture}
\end{equation}
where $\wV_i\in\R^{(l_i+1)\times l_{i+1}}$ is the weight matrix of the $i\textsuperscript{th}$ layer, and $\act_i: \R^{l_i}\to\R^{l_i+1}$ represents the activation function of the $i\textsuperscript{th}$ layer. 
The activation function is defined as $\act_i(\mv x)=[\sigma(x_1),\sigma(x_2),\cdots, \sigma(x_{l_{i}}), 1]^\top,\ \forall\mv x\in\R^{l_i}$, where $\sigma: \R\to\R$ is a nonlinear function, and the augmentation of $1$ is used to account for bias terms in the weight matrices. 
Notice that the output size of $\NN(\cdot)$ is the same as that of the control input $\mv\tau$ (\ie $l_{k+1}=n$).

@@

\begin{remark}
    Assumption \ref{assum:convex} is not restrictive, since the saturation functions are convex in practice including the origin.
    Moreover, Assumption \ref{assum:LICQ} is a standard assumption in optimization problems, which ensures that the gradients of the active constraints are linearly independent.
    This assumption will be used in the stability analysis (see, Lemma \ref{lem:convex:angle}).
\end{remark}

@@

The weight constraints are essential to prevent the weights from diverging during the adaptation process.
The weight constraints $\boldsymbol{c}_{\theta}:= [c_{\theta_i}]_{i\in[0,\cdots ,k]}\in\mathbb R^{k+1}$ are defined for each layer's weight as follows:
\begin{equation}
    c_{\theta_i}
    =
    \tfrac{1}{2}
    (
        \Vert \estwth_i\Vert^2 
        -
        \bar\theta_i^2 
    )    
    \le 0
    \label{eq:cstr:weight_ball}
\end{equation}
with $\bar\theta_i<\infty$ denoting the maximum allowable norm for $\estwth_i$. 
The gradient of $\boldsymbol{c}_\theta$ with respect to $\estwth$ is given by
\begin{equation}
    \pptfrac{c_{\theta_i}}{\estwth_j} 
    =
    \begin{cases}
        \estwth_i,
        &
        \text{if } i=j
        \\
        \mv{0},
        &
        \text{if } i\ne j
        .
    \end{cases} 
    \label{eq:cstr:weight_ball:grad}
\end{equation}
Note that $\mv c_{\theta}$ satisfies Assumption \ref{assum:convex} and \ref{assum:LICQ} invoking Lemma \ref{lem:convex:angle} and \eqref{eq:cstr:weight_ball:grad}, respectively.

@@

Since, here, the control input constraints are inactive, $\mysat(\cdot)$ in \eqref{eq:lya1:dot2} and $c_j,\ \forall j\in\mathcal{I}$ in \eqref{eq:lya2:dot} can be removed.
Consider the Lyapunov function candidate $V_3:=V_1+V_2$ and its time derivative:
\begin{equation}
    \begin{aligned}
        \ddtt V_3
        =&
        -\lambda_{\text{min}}(\mm K)\norm{\fe}^2
        +\bar\tau_d\norm{\fe}
        +\fe^\top (\estNN - \idealNN - \mv\epsilon)
        \\
        &
        -\estwth_k^\top (
            (\mm I_{l_{k+1}}\otimes \hat\act_k^\top)^\top
            \fe
            +
            \lambda_{\theta_k}\estwth_k
        )
        \\
        \le&
        -\lambda_{\text{min}}(\mm K)\norm{\fe}^2
        +\fe^\top \estNN
        +(
            \bar\tau_d+\norm{
                \underbrace{
                    \idealNN+\mv\epsilon
                }_{=\mv\tau^*}
            }
        )
        \norm{\fe}
        \\
        &
        -\estNN^\top\fe 
        -\lambda_{\theta_k}\norm{\estwth_k}^2
        \\
        \le&
        -\lambda_{\text{min}}(\mm K)\norm{\fe}^2
        +(\bar\tau_d+\bar\tau)
        \norm{\fe}
        -\lambda_{\theta_k}\norm{\estwth_k}^2
        .
    \end{aligned}
    \label{eq:lya3:dot}
\end{equation}
Like in Case (C$_1$), the boundedness of $\fe$ can be verified by the invariant sets $\Theta_{\fe}^{c_2}$ defined as
\begin{equation}
    \Theta_{\fe}^{c_2}
    =
    \left\{ 
        \fe \in \R^n 
        \mid 
        \norm{\fe} 
        \le 
        \tfrac{
            \bar\tau_d+\bar\tau
        }{
            \lambda_{\text{min}}(\mm K)
        }
    \right\}
    .
\end{equation}
The boundedness of $\estwth_k$ also can be ensured by the invariant set $\Theta_{\theta_k}^{c_2}=\{ \estwth_k \in \R^{\Xi_{k}} \mid \norm{\estwth_k} \le \bar\theta_k \}$, as $\lambda_{\theta_k}$ exists positive until $c_{\theta_k}$ is satisfied.

@@

The proposed CoNAC was validated using a two-link manipulator model, as depicted in Fig.~\ref{fig: manipulator}, adapted from \cite{Markus:2013aa}. 
The parameters $q_p,{q_d}_p,\tau_p,m_p,l_p,{l_c}_p,b_p$ and ${f_c}_p$ denote the joint angle, desired joint angle, torque, mass, length, center of mass, viscous coefficient, and friction coefficient, respectively, for link $p\in[1,2]$.
%This model contains terms of gravity and friction in its mechanical system.
%These terms make system functions in \eqref{eq. system dynamics 1} nonlinear.
%and can be considered as the disturbance of the system.
The values of the system model parameters are provided in Table~\ref{table: system parameters}. The desired trajectory for $\q=[q_1,q_2]^\top $ was defined as
\begin{equation}
    {q_d}(t) = 
    \begin{bmatrix}
        {q_d}_1\\{q_d}_2
    \end{bmatrix}
    =
    \begin{bmatrix}
        +\cos(0.5\pi t) + 1 \\
        -\cos(0.5\pi t) - 1 
    \end{bmatrix}.
\end{equation}
%\color{red}
%Considering the power limitation of the power source for the actuators [], 
The control input saturation function was defined as $h(\tau):= \tau/\Vert\tau\Vert \cdot \text{SSF}_L^U(\Vert\tau\Vert)$, where smooth saturation function (SSF) was adopted from \cite{Vasquez-Plaza:2023aa} and is given by
\begin{equation}
    \text{SSF}_L^U(\Vert\tau\Vert) = {\Vert\tau\Vert\over (1+(\Vert\tau\Vert/\bar\tau)^p)^{1/p}}.
    \label{eq. h func}
\end{equation}
with $p$ being the smoothing factor. The effect of $p$ and the boundedness of $\Vert\partial h/\partial \tau\Vert_F$ is shown in Fig.~\ref{fig: h func}.
The parameters of the control input saturation function were selected as $p=100$ and $\bar\tau=50$.

@@

\begin{table}[!t]
    \renewcommand{\arraystretch}{1.3}
    \caption{System model parameters.}
    \centering
    \begin{tabular}{c m{11em} c c c }
    \hline
    \textbf{Symbol} & \textbf{Description} & \textbf{Link 1} & \textbf{Link 2} \\
    \hline
    \hline 
    $m_p$ & Mass of $p\textsuperscript{th}$ link    & 23.902 (kg) & 3.88 (kg) \\
    \hline
    $l_p$  & Length of $p\textsuperscript{th}$ link   & 0.45 (m) & 0.45 (m) \\
    \hline
    ${l_c}_p$ & COM of $p\textsuperscript{th}$ link  & 0.091 (m) & 0.048 (m) \\
    \hline
    $b_p$   & Viscous coef. of $p\textsuperscript{th}$ link  &  2.288 (Nms) & 0.172 (Nms) \\
    \hline
    ${f_c}_p$  & Friction coef. of $p\textsuperscript{th}$ link &  7.17 (Nm) & 1.734 (Nm) \\
    \hline
    \end{tabular}
    \label{table: system parameters}
\end{table}

@@

@@

\begin{comment}
    The tracking results of the selected controllers are shown in Fig.~\ref{fig: tracking}.
    To demonstrate the effectiveness of using DNNs for compensating the lumped system uncertainty function $f$, the gains ${k_q}$ and ${k_z}$ for BSC were intentionally selected as small values, resulting in a weak ability to handle these uncertainties. As a result,
    %poor performance and sufficiently large values to satisfy \eqref{eq. ctrl stable condition}.
    %the parameters of CM1 are poorly tuned, 
    BSC failed to track the reference trajectory, as shown in Fig.~\ref{fig: tracking_CM1}.

@@

    %Since it is generally known that the deeper NNs have better approximation performance with less computation cost, the NNs should have more layers.
    %However, because the NNs in this paper utilize $\tanh(\cdot)$ as the activation function, the NNs have the gradient vanishing problem as shown in Fig.~\ref{fig: weight_CM2}-\ref{fig: weight_CoNAC}. (\ie the weight updates are smaller as its layer is closer to the input layer.)
    %To address this issue, the activation function should be selected as the ReLU or the Leaky ReLU, while ensuring the stability of the controller.
\end{comment}

@@

Most physical systems have control input limits due to electrical and mechanical limitations. These are expressed as $\boldsymbol{c}_{\overline \tau}:= [c_{\overline \tau_i}]_{i\in[1,\cdots,n]}$ and $\boldsymbol{c}_{\underline\tau}:= [c_{\underline\tau_i}]_{i\in[1,\cdots,n]}$, where
\begin{equation}
    \begin{aligned}
        c_{\overline \tau_i}=\tau_{(i)} - {\tau_{\overline \tau_i}} \le 0
        \\
        c_{\underline\tau_i}={\tau_{\underline\tau_i}}-\tau_{(i)} \le 0
    \end{aligned}
    \label{eq. cstr input saturation}
\end{equation}
with $\tau_{\overline \tau_i}$ and $\tau_{\underline\tau_i}$ representing the maximum and minimum control input bounds, respectively.
% The corresponding Lagrange multipliers are $\lambda_{u_j,i},\ \forall j\in[M,m]$. 
The gradients of $\boldsymbol{c}_{\overline \tau}$ and $\boldsymbol{c}_{\underline\tau}$ with respect to $\estwth$ are given by
\begin{equation}
    \begin{aligned}
        \pptfrac{\boldsymbol c_{\overline \tau}}{\estwth}
        =& 
        % \begin{bmatrix}
        %     \pptfrac{c_{\overline \tau_1}}{\estwth}^\top \\
        %     \vdots \\
        %     \pptfrac{c_{\overline \tau_n}}{\estwth}^\top
        % \end{bmatrix}
        = 
            -\pptfrac{\estNN}{\estwth}
        %     \\
        % =&
        =
        -\begin{bmatrix}
            (I_{l_{k+1}}\otimes \estNN_{k}^\top)&
            \!\cdots\! &
            (
                \cdot
            )
        \end{bmatrix} 
        \in
        \mathbb R^{n\times \Xi}
        , 
        \\
        \pptfrac{\boldsymbol c_{\underline\tau}}{\estwth}         
        :=
        & 
        % \begin{bmatrix}
        %     \pptfrac{c_{\underline\tau_1}}{\estwth}^\top \\
        %     \vdots \\
        %     \pptfrac{c_{\underline\tau_n}}{\estwth}^\top
        % \end{bmatrix}
        = 
        +\pptfrac{\estNN}{\estwth}
        % \\
        % =&
        =
        +\begin{bmatrix}
            (I_{l_{k+1}}\otimes \estNN_{k}^\top)&
            % V_k^\top \phi_{k}' (I_{l_{k}}\otimes  \phi_{k-1}^\top)&
            \!\cdots\! &
            (
                \cdot
            )
        \end{bmatrix} 
        \in
        \mathbb R^{n\times \Xi}
        .
    \end{aligned}
    \label{eq. nabla input sat}
\end{equation}

@@

Consider the control input $\tau$ as the torque of each actuator corresponding to its generalized coordinate. Since torque is typically linearly proportional to current, actuators that share a common power source are often subject to total current limitations. This can be captured by the following inequality constraint: 
\begin{equation}
    c_{u}=\norm{\mv{\tau}}^2 -\bar\tau^2  \le 0
    \label{eq. cstr input ball}
\end{equation}
with $\bar\tau\in\R_{>0}$ denoting the maximum allowable control input magnitude. This input norm constraint is also commonly applied in current and torque control problems for electric motors \cite{Choi:2024aa}.
% The corresponding Lagrangian multipier is $\lambda_{u_b}$. 
The gradients of $c_{u}$ with respect to $\estwth$ are given by
\begin{equation}
    \pptfrac{\boldsymbol c_{u}}{\estwth}
    \!=\! 
    -\textstyle\sum_{i=1}^n 2\tau_{(i)} 
    \left(
        \myrow_i
        (
            -\pptfrac{\estNN}{\estwth}
        )
    \right)^\top  
    \!=\! 
    \tau^\top (I_{l_{k+1}}\otimes \estNN_k^\top)
    \in \mathbb R^{\Xi}.
    \label{eq. nabla input ball}
\end{equation}
It should be noted that constraints \eqref{eq. cstr input saturation} and \eqref{eq. cstr input ball} cannot be imposed simultaneously, as their gradients \eqref{eq. nabla input sat} and \eqref{eq. nabla input ball} are linearly dependent, violating the LICQ condition.
